The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-02-11 paper/ms.tex
fixing small things

\begin{figure*}
\begin{center}
  \includegraphics[width=1.0\textwidth]{f1.eps}
\end{center}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
    the central (homogeneous) photon distribution. All photons were
    taken into  account regardless of their final direction of propagation.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

In the next subsections we characterize the line morphology by
the half-width at half intensity and the peak maxima. In order to
interpret the morphological changes in the line we also report the
median number of scatter for each \ly photon in the
simulation. For the models where dust is included we measure the 
escape fraction as a function of rotational velocity. Finally, we make
an estimate of the anisotriopic emission of the models in comparison
with static spheres.

@@

We parameterize the dependency of the linewidth as $W^2 =
W_{0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity witdth can be expressed as a
quadratic sum of the two relevant velocities in the problem. We find
that for $\lambda = 3.895$ ($\lambda= 1.982$) for the central
(homogeneous) sources.

@@

\item The line width increases with rotational velocity. The line with
  approximately follows the functional form $W^2 = W_{
    0}^2 + (V_{\rm max}/\lambda)^2$ where $W_{0}$ indicates the line
  width for the static case. $\lambda$ is a constat determined from
  the radiative transfer results it is $\lambda_{\rm c}=XX$ and
  $\lambda_{\rm h}=YY$ for the central and homogeneous source
  distribution, respectively.

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=1.0\textwidth]{f1.eps}
\end{center}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions in all the models. The continous (dashed) line represents the 
    central (homogeneous) source distributions.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

In the next subsections we characterize the line morphology by
the full width at half maximum (FWHM) and the location of the peak maxima. In order to interpret the morphological changes in the line we also report the
median number of scatter for each \ly photon in the
simulation. For the models where dust is included we measure the 
escape fraction as a function of rotational velocity. Finally, we make
an estimate of the anisotriopic emission of the models in comparison
with static spheres.

@@

We parameterize the dependency of the linewidth as $W^2 =
W_{0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity width can be expressed as a
quadratic sum of the two relevant velocities in the problem. By
fitting simultaneously all the data points corresponding to central
and homogeneous models we find $\lambda_{\rm c} = 3.9 \pm$ and
$\lambda_{\rm h}= 1.9\pm $ respectively.

@@

\item The line width increases with rotational velocity. The line with
  approximately follows the functional form $W^2 = W_{
    0}^2 + (V_{\rm max}/\lambda)^2$ where $W_{0}$ indicates the line
  width for the static case. $\lambda$ is a constat determined from
  the radiative transfer results it is $\lambda_{\rm c}=3.9\pm$ and
  $\lambda_{\rm h}=1.9\pm$ for the central and homogeneous source
  distribution, respectively.
